---
title: "Tugasan 4 "
output:
  pdf_document: default
---

1\. Janakan data mtcars dalam R

```{r, echo=T, include=TRUE}
data = mtcars
head(mtcars,10)
```

2. Skalakan data tersebut.

```{r}
mtcars_scaled = scale(mtcars)
head(mtcars_scaled,10)
```

3. Jalankan analisis faktor untuk menurunkan dimensi data mtcars.

```{r, echo=T, include=T}
library(corrplot)
corrplot(cor(mtcars_scaled), order='hclust')
```

```{r, echo=T, include=T}
library(psych)
scree(mtcars_scaled)
```

4. Kenalpasti faktor pendam yang sesuai yang boleh menerangkan data asal.

```{r, echo=T, include=T}
F.A = factanal(mtcars_scaled, factors=3, scores = 'regression',rotation='varimax')
F.A
```

```{r, echo=T, include=T}
head(F.A$scores,20)
```

5. Berikan tafsiran yang bersesuaian bagi setiap faktor pendam terhadap data asal.

### **Factor 1:** seems to be related to **performance** vehicle

-   High positive loadings:

    -   Rear axle ratio (0.804)

    -   Transmission (0.880)

    -   Number of forward gears (0.908)

-   Moderate negative loadings:

    -   Miles/(US) gallon (-0.643)

    -   Displacement (-0.719)

    -   Weight (-0.778)

### **Factor 2:** reflects **engine characteristics and power**

-   High positive loadings:

    -   Number of cylinders (0.703)

    -   Gross horsepower (0.725)

    -   1/4 mile time (-0.946)

-   Moderate negative loadings:

    -   Engine Shape (-0.805)

### **Factor 3:** seems to reflect **heavier, less fuel-efficient vehicles**

-   High positive loadings:

    -   Weight (0.524)

    -   Number of carburetors (0.719)

-   Moderate negative loadings:

    -   Miles (-0.473)

    -   Gross horsepower (0.513)

### **Summary of Factors:**

1.  **Factor 1** seems to be related to **performance** vehicles, with manual transmissions, higher gear ratios, and larger engine sizes that are less fuel-efficient.

2.  **Factor 2** reflects **engine characteristics and power**, including high horsepower and large engine displacement, likely representing powerful vehicles with a focus on engine strength rather than fuel efficiency or acceleration speed.

3.  **Factor 3** seems to reflect **heavier, less fuel-efficient vehicles** with potentially more complex carburetor systems and greater emphasis on weight and engine characteristics rather than speed or fuel economy.
