---
title: "Class 1"
output:
  pdf_document: default
  html_document: default
editor_options: 
  markdown: 
    wrap: 72
---

## Libraries Used

```{r echo=T, include=T}
library(dplyr)
library(stringr)
library(lubridate)
library(DataCombine)
```

# Upload data into R Studio

```{r echo=TRUE}
knitr::opts_chunk$set(echo=T)
# getwd()
# setwd(dir = "E:/MSc DSc/Sem 1/Business Analytics/Ch1_bike_sharing_data.csv")
datch1= read.csv("E:/MSc DSc/Sem 1/Business Analytics/Ch1_bike_sharing_data.csv")
head(datch1,10)
str(datch1)
```

# Transforming data

## Using logical expression

extracted_rows gives info on no of rows and cols

```{r echo=T}
extracted_rows = filter(datch1, registered == 0, season == 1 | season == 2) 
dim(extracted_rows)
```

```{r}
using_membership = filter(datch1, registered == 0, season %in% c(1,2)) 
identical(extracted_rows, using_membership)
```

## Adding calculated column

```{r echo=T}
add_revenue = mutate(extracted_rows, revenue = casual*5)

head(add_revenue,10) 
```

## Aggregate Data

```{r}
grouped = group_by(add_revenue,season) 
head(grouped,10)
```

## Export Data

```{r eval=FALSE}
report = summarise(grouped, Casual = sum(casual), Revenue = sum(revenue)) 
report
write.csv(report, "revenue_report.csv", row.names = FALSE) 
write.table(report, "revenue_report.txt", row.names = FALSE)
```

# Exercise Chapter 1 Bike

## Load the dataset

```{r}
bike = read.csv("E:/MSc DSc/Sem 1/Business Analytics/Ch2_raw_bikeshare_data.csv") 
head(bike,10) 
```

```{r}
str(bike)
```

## Tabulate the null values

```{r}
table(is.na(bike))
```

## Finding and fixing flawed data

```{r}
bad_data = str_subset(bike$humidity, '[a-z A-Z]')
bad_data
location = str_detect(bike$humidity, bad_data) 
bike[location,]
```

```{r}
bike$humidity = str_replace_all(bike$humidity, bad_data, "61") 
table(is.na(bike)) 
```

```{r}
str(bike) 
```

```{r}

bike$humidity = as.numeric(bike$humidity) 
```

## Transform and converting datatypes

```{r}
bike$holiday = factor(bike$holiday, levels = c(0,1),
                        labels = c("no","yes"))
bike$workingday = factor(bike$workingday, levels = c(0,1),
                        labels = c("no","yes"))
bike$weather = factor(bike$weather, levels = c(1,2,3,4),
                        labels = c("clr_part_cloud",
                                    "mist_cloudy",
                                    "lt_rain_snow",
                                    "hcy_rain_snow"),
                        ordered = TRUE)
bike$season = factor(bike$season, levels = c(1,2,3,4),
                        labels = c("spring","summer",
                                    "fall","winter"),
                        ordered = TRUE)
bike$datetime = mdy_hm(bike$datetime)
```

## Adapting data to standard

```{r}
unique(bike$sources)
```

```{r}
bike$sources = tolower(bike$sources)
bike$sources = str_trim(bike$sources)
na_loc = is.na(bike$sources)
bike$sources[na_loc] = "unknown"
```

## Combining data to new categories

```{r}
web_sites = "(www.[a-z]*.[a-z]*)"
current = unique(str_subset(bike$sources, web_sites))
current

```

```{r}
replace = rep("web", length(current))
replace
```

```{r}
replacements = data.frame(from = current, to = replace)
replacements
```

```{r}
bike = FindReplace(data = bike, Var = "sources", replacements, from = "from", to = "to", exact = FALSE)
unique(bike$sources)
```

```{r}
bike$sources = as.factor(bike$sources)
str(bike$sources)
```
