---
title: "Class 4 - Time Series Analysis"
output:
    pdf_document: default
knitr:
  opts_chunk: 
    echo: true
    include: true
    message: false  # Optional: Hide messages
    warning: false  # Optional: Hide warnings
---

# ARIMA

Assumption :

-   Stationary Data : mean and variance does not change as a function of time

-   Differencing technique:

$$
y/_diff/_trend = y_{(t+1)}-y_t
$$

$$
y/_diff/_seasonal = y_{(t + lag)}-y_t
$$

```{r, include=F}
library(tidyverse)
```

## 1. Load Dataset

```{r}
cycle = read.csv("G:/My Drive/Master-Data-Science/Semester_1/Business_Analytics/Data/Ch6_ridership_data_2011-2012.csv")
head(cycle)
```

## 2. Aggregate by month

```{r}
monthly_ride = as.data.frame(cycle %>%
                               group_by(year = year(datetime), month = month(datetime)) %>%
                               summarise(riders = sum(count)))
head(monthly_ride)
```

```{r}
table(monthly_ride$year, monthly_ride$month)
```

## 3. Convert to TS data

```{r}
riders = monthly_ride[,3]
monthly = ts(data = riders, start = c(2011,1), end = c(2012,12), frequency = 12)
monthly
```

## 4. Decompose the data

```{r}
plot(decompose(monthly))
```

## 5. Difference the data (if needed)

```{r}
plot(monthly , type = 'b', main='Monthly')
```

```{r}
plot(diff(monthly), main = 'diff(monthly)')
# Remove trend pattern in data, remain seasonality+constant+randomness
```

```{r}
plot(diff(diff(monthly), lag=12), main='diff(diff(monthly), lag=12)')
# Remoce trend and seasonal pattern in data, remain constant+randomness
```

## 6. Generate ACF and PACF

```{r}
par(mfrow=c(1,2))
acf(monthly)
pacf(monthly)
par(mfrow=c(1,1))
```

The values have to be whole numbers, therefore inadequate data to use for prediction. Possible values:

-   p : 0,1,2

-   d : 0,1

-   q : 0,1

## 7. Run ARIMA Model

```{r fig.height=10, fig.width=10}
arima100_000 = arima(monthly, c(1,0,0),
                    seasonal = list(order = c(0,0,0)))
arima100_000
tsdiag(arima100_000)
```

```{r fig.height=10, fig.width=10}
arima110_000 = arima(monthly, c(1,1,0),
                    seasonal = list(order = c(0,0,0)))
arima110_000
tsdiag(arima110_000)
```

```{r fig.height=10, fig.width=10}
arima210_000 = arima(monthly, c(2,1,0),
                    seasonal = list(order = c(0,0,0)))
arima210_000
tsdiag(arima210_000)
```

```{r fig.height=10, fig.width=10}
arima110_010 = arima(monthly, c(1,1,0),
                    seasonal = list(order = c(0,1,0)))
arima110_010
tsdiag(arima110_010)
```

```{r fig.height=10, fig.width=10}
arima011_000 = arima(monthly, c(0,1,1),
                    seasonal = list(order = c(0,0,0)))
arima011_000
tsdiag(arima011_000)
```

```{r}
data.frame(
  Model = c("ARIMA(1,0,0)(0,0,0)",
            "ARIMA(1,1,0)(0,0,0)",
            "ARIMA(2,1,0)(0,0,0)",
            "ARIMA(1,1,0)(0,1,0)",
            "ARIMA(0,1,1)(0,0,0)"),
  AIC = c(arima100_000$aic,
          arima110_000$aic,
          arima210_000$aic,
          arima110_010$aic,
          arima011_000$aic),
  Diagnostics = c("Poor residuals and poor p-values",
                  "Good diagnostics",
                  "Good diagnostics",
                  "Poor p-values",
                  "Poor p-values")
)
```

## 8. Run forecasting

```{r}
library(forecast)
yr_forecast = forecast(arima110_000, h=12)
plot(yr_forecast)
```

# TBATS

```{r}
monthly_data = tbats(monthly)
  
year_forecast = forecast(monthly_data, h=12)
plot(year_forecast)
```

Look at data

```{r}
summary(year_forecast$mean)
```

```{r}
summary(year_forecast$upper)
```

```{r}
summary(year_forecast$lower)
```

Create annotations

```{r}
mean_2011 = round(as.numeric(filter(monthly_ride, year == 2011) %>%
                               summarise(mean = mean(riders))),0)
mean_2012 = round(as.numeric(filter(monthly_ride, year == 2012) %>%
                               summarise(mean = mean(riders))),0)
mean_2013 = round(mean(year_forecast$mean))
max_mean_2013 = round(max(year_forecast$mean))
```

Create complete graph

```{r}
# Main plot
plot(year_forecast)

# line segments
abline(h = max(year_forecast$mean), lty=2, col='blue')
segments(2011, mean_2011, x1 = 2012, y1 = mean_2011, col = 'darkgrey', lty = 2, lwd = 2)
segments(2012, mean_2012, x1=2013, y1=mean_2012, col='darkgrey', lty=2,lwd=2)
segments(2013, mean_2013, x1=2014, y1=mean_2013, col='blue', lty=2, lwd=2)

# Annotation
text(2011.12, mean_2011 + 10000, mean_2011)
text(2012, mean_2012 + 10000, mean_2012)
text(2013, mean_2013 + 10000, mean_2013)
text(2013, max_mean_2013 + 10000, paste("Max mean :", max_mean_2013))
```
