---
title: "Class 7 - Association Rule"
output:
    pdf_document: default
knitr:
  opts_chunk: 
    echo: true
    include: true
    message: false  # Optional: Hide messages
    warning: false  # Optional: Hide warnings
editor_options: 
  markdown: 
    wrap: 72
---

A -\> B, or B given A

1.  Support $P(A \cap B)$

2.  Confidence $P(B|A) = \frac{P(A \cap B)}{P(A)}$

3.  Lift $P(A|B) = \frac{P(A \cap B)}{P(A)*P(B)}$

**Apriori**

1.  Frequent Itemsets: These are sets of items that appear together in a
    transaction more frequently than a specified threshold (called
    support).
2.  Association Rules: These are rules of the form {A} → {B}, where:
    -   A is an item or itemset (e.g., "Bread"),
    -   B is another item or itemset (e.g., "Butter").
    -   The rule suggests that if A is bought, Bis likely to be bought
        as well.

```{r}
library(arules)
library(arulesViz)
```

```{r}
data(Groceries)
head(Groceries)
```

```{r}
summary(Groceries)
```

```{r}
inspect(head(Groceries))
```

```{r}
rules = apriori(Groceries, parameter = list(support = 0.05, confidence = 0.1))
sorted_rules = sort(rules, by='lift', decreasing=T)
inspect(sorted_rules)
```

```{r}
plot(sorted_rules, method='graph')
```

```{r}
itemFrequencyPlot(Groceries, topN=10)
```

```{r}
library(ggplot2)
plot(sorted_rules,
  method = "graph",
  control = list(
    edges = ggraph::geom_edge_link(
      end_cap = ggraph::circle(4, "mm"),
      start_cap = ggraph::circle(4, "mm"),
      color = "green",
      arrow = arrow(length = unit(2, "mm"), angle = 20, type = "closed"),
      alpha = .8
    ),
    nodes = ggraph::geom_node_point(aes(size = support, color = lift)),
    nodetext = ggraph::geom_node_label(aes(label = label), alpha = .8, repel = TRUE)
  ),
  limit = 10
) +
  scale_color_gradient(low = "blue", high = "red") +
  scale_size(range = c(2, 10))
```
